Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-12 alloscore_manuscript/alloscore-application.Rnw
trimming long bibliography authorships. closes #76.

\usepackage{natbib}
\bibliographystyle{unsrtnat}

@@

<<multi-k-scores, results='asis'>>=
left_join(ias, as) |>
  rename(`IAS centered at 15k` = IAS_wt,
         `IAS uniform` = IAS) |>
  arrange(-`IAS centered at 15k`) |>
  xtable::xtable(caption = "Allocation scores shown in Figure \\ref{fig:multi-k}C, sorted by Integrated Allocation Scores (IAS) centered at 15,000.",
                 digits = 0,
                 label = "tab:multi-k-scores") |>
  print(include.rownames = FALSE, )
@

>>>>

\usepackage{natbib}
\bibliographystyle{unsrtnat-abbr}

@@

<<multi-k-scores, results='asis'>>=
left_join(ias, as) |>
  rename(`IAS centered at 15k` = IAS_wt,
         `IAS uniform` = IAS) |>
  arrange(`IAS centered at 15k`) |>
  xtable::xtable(caption = "Allocation scores shown in Figure \\ref{fig:multi-k}C, sorted by Integrated Allocation Scores (IAS) centered at 15,000.",
                 digits = 0,
                 label = "tab:multi-k-scores") |>
  print(include.rownames = FALSE, )
@
